Deterministic Scheduling of Periodic Messages in a Network

### 2017-07-12 article/article.tex

\todo{citation [7] pour les reseaux points a points ?}
 In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. 
 Statistical multiplexing even with a large bandwidth does not comply with the latency requirements. Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits. Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches. This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations. 
 %Hence a solution is needed to offer low latency over cheap packet based networks. 
 Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}. The aim is to operate a C-RAN on a low-cost shared switched network.

@@

  \paragraph*{Acknowledgments} The authors thanks Christian Cadere and David Auger for the friendly discussions
  they had on the subject and their insightful remarks.

>>>>

\todo{citation [7] pour les reseaux points a points ?}
 In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. 
 Statistical multiplexing even with a large bandwidth does not comply with the latency requirements. Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits. Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches. This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations. Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}. The aim is to operate a C-RAN on a low-cost shared switched network.

@@

  \paragraph*{Acknowledgments} The authors thanks Christian Cad\'er\'e and David Auger for the friendly discussions
  they had on the subject and their insightful remarks.
